### 2018-01-20 includes/introduction.tex
Addressing Federico's feedback.

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and useful in practice. \theSolvers{}\cite{cvc4}\cite{z3str3} are \numSolvers{} such solvers. Moreover a standard input language for problem instances, \smt{}\cite{smt}, has been developed and many solvers support it. To validate their solvers, many authors have relied on hand-crafted input suites or real-world examples from industrial applications \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}. Indeed several suites of industrial and hand-crafted problems have been compiled \cite{kaluza} \cite{kausler} to both verify solvers and benchmark their performance. However though these suites help solver developers debug and verify their solvers, they do not age well. As solvers grow more complex and expressive, fixed benchmarks fail to exercise those new behaviours. As a result, more and more solver functionality goes untested or unverified.

    We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory verification tool. We show its effectiveness by presenting defects we were able to find in leading solvers.

>>>>

    Many SMT solvers that support the theory of strings have been developed over the past decade, and several have matured to the point of being performant and useful in practice. \theSolvers{}\cite{cvc4}\cite{z3str3} are \numSolvers{} such solvers. Moreover a standard input language for problem instances, \smt{}\cite{smt}, has been developed and many solvers support it. To validate their solvers, many authors have relied on hand-crafted input suites or real-world examples from industrial applications \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}. Indeed several suites of industrial and hand-crafted problems have been compiled \cite{kaluza} \cite{kausler} to both validate solvers and benchmark their performance. However, though these suites help debug solvers, they do not age well. As solvers continue to grow, fixed benchmarks leave more and more functionality untested.

    We introduce a modular fuzzer for string solvers, \fuzzer{}, and describe its utility as an exploratory validation tool. We show its effectiveness by presenting defects we were able to find in leading solvers.

### 2018-01-20 includes/prior.tex
Addressing Federico's feedback.

    Naturally, many solver developers author their own unit test suites to verify their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}. In addition, several popular problem suites are publicly available for solver verification, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.

>>>>

    Naturally, many solver developers author their own unit test suites to validate their solvers \cite{cvc4-tests} \cite{z3str3-tests} \cite{z3str2-tests}. In addition, several popular problem suites are publicly available for solver validation, such as the Kaluza \cite{kaluza} and Kausler \cite{kausler} suites.
